---
title: "accidenttracker Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{accidenttracker Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(accidenttracker)
```

The function of this package is to load the US_Accidents data set as a component of the accident_tracker shiny application. The data set has been adjusted to only include data for the year of 2019 in order to allow the file to be compatible with file size limits with github. 

List of Removed Columns
---
- Airport_Code
- Description
- Number
- Street
- Country
- Civil_Twilight
- Nautical_Twilight
- Astronomical_Twilight


List of Changes to Data Set
---
- Filtered all data to only include points from the year 2019.

- Column names were changed in order to be in compliance with the style guide for MICR 475.
  - The names for each column were changed to the proper forms of snake case. 

- Missing values were removed from the data set via the 'dplyr::filter' command.

- Information pertaining to weather data was originally spread over numerous smaller columns. 
  - Specific weather conditions, such as "Fair" and "Heavy Rain", were categorized into broader weather descriptions in a new column. 
  - Conditions directly related to "Rain", "Snow", "Windy", etc. were grouped together for ease of visual and graphical interpretation 
  

Select Input and Select Options
---
These two functions for analytically filtering and interfacing with the US Accidents data set. 
Both functions utilize an "if" loop to determine their output

- select_input
  - Utilizes an if loop to generate a shiny widget which allows users to select different choices of variables to view the data set through. Examples of these include "color", "Day/Night" etc. 
  
- select_options
  - This function exists to generate a unique character vector from a selected column when viewing the data through the shiny app. 
  
